\Title

### 2020-03-12 manuscript/manuscript.tex
Define parameters as ranges and improve parameters table (#35)
Define gridding parameters as ranges when possible. Rewrite functions to
convert parameters to LaTeX variables using \numlist and \numrange. Change
parameters table design, showing values as ranges when possible. Include
damping parameters on table. Merge best predictions parameters and R2 scores
into the parameters tables.

\begin{table*}
    \centering
    \caption{
        Combination of parameters that produce the best prediction when
        gridding the synthetic ground survey with each source distribution.
        The score of each best prediction is also shown.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources below data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (m) & \BestGroundSourceBelowDataConstantDepthDepth
                   & \BestGroundBlockMedianSourcesConstantDepthDepth
                   & \BestGroundGridSourcesConstantDepthDepth \\
        Spacing (m) & -
                     & \BestGroundBlockMedianSourcesConstantDepthSpacing
                     & \BestGroundGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \BestGroundGridSourcesConstantDepthPad \\
        Damping & \BestGroundSourceBelowDataConstantDepthDamping
                & \BestGroundBlockMedianSourcesConstantDepthDamping
                & \BestGroundGridSourcesConstantDepthDamping \\
        \textbf{R$^2$ score}
                & \textbf{\BestGroundSourceBelowDataConstantDepthScore}
                & \textbf{\BestGroundBlockMedianSourcesConstantDepthScore}
                & \textbf{\BestGroundGridSourcesConstantDepthScore} \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestGroundSourceBelowDataRelativeDepthDepth
                   & \BestGroundBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (m) & -
                & \BestGroundBlockMedianSourcesRelativeDepthSpacing
                & \\
        Damping & \BestGroundSourceBelowDataRelativeDepthDamping
                & \BestGroundBlockMedianSourcesRelativeDepthDamping
                & \\
        \textbf{R$^2$ score}
                & \textbf{\BestGroundSourceBelowDataRelativeDepthScore}
                & \textbf{\BestGroundBlockMedianSourcesRelativeDepthScore}
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestGroundSourceBelowDataVariableDepthDepth
                   & \BestGroundBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \BestGroundSourceBelowDataVariableDepthDepthFactor
                     & \BestGroundBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \BestGroundSourceBelowDataVariableDepthKNearest
                  & \BestGroundBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (m) & -
                     & \BestGroundBlockMedianSourcesVariableDepthSpacing
                     & \\
        Damping & \BestGroundSourceBelowDataVariableDepthDamping
                & \BestGroundBlockMedianSourcesVariableDepthDamping
                &  \\
        \textbf{R$^2$ score}
                & \textbf{\BestGroundSourceBelowDataVariableDepthScore}
                & \textbf{\BestGroundBlockMedianSourcesVariableDepthScore}
                & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Combination of parameters that produce the best prediction when
        gridding the synthetic airborne survey with each source distribution.
        The score of each best prediction is also shown.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources below data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (m) & \BestAirborneSourceBelowDataConstantDepthDepth
                   & \BestAirborneBlockMedianSourcesConstantDepthDepth
                   & \BestAirborneGridSourcesConstantDepthDepth \\
        Spacing (m) & -
                     & \BestAirborneBlockMedianSourcesConstantDepthSpacing
                     & \BestAirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \BestAirborneGridSourcesConstantDepthPad \\
        Damping & \BestAirborneSourceBelowDataConstantDepthDamping
                & \BestAirborneBlockMedianSourcesConstantDepthDamping
                & \BestAirborneGridSourcesConstantDepthDamping \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBelowDataConstantDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesConstantDepthScore}
                & \textbf{\BestAirborneGridSourcesConstantDepthScore} \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestAirborneSourceBelowDataRelativeDepthDepth
                   & \BestAirborneBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (m) & -
                & \BestAirborneBlockMedianSourcesRelativeDepthSpacing
                & \\
        Damping & \BestAirborneSourceBelowDataRelativeDepthDamping
                & \BestAirborneBlockMedianSourcesRelativeDepthDamping
                & \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBelowDataRelativeDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesRelativeDepthScore}
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (m) & \BestAirborneSourceBelowDataVariableDepthDepth
                   & \BestAirborneBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \BestAirborneSourceBelowDataVariableDepthDepthFactor
                     & \BestAirborneBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \BestAirborneSourceBelowDataVariableDepthKNearest
                  & \BestAirborneBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (m) & -
                     & \BestAirborneBlockMedianSourcesVariableDepthSpacing
                     & \\
        Damping & \BestAirborneSourceBelowDataVariableDepthDamping
                & \BestAirborneBlockMedianSourcesVariableDepthDamping
                &  \\
        \textbf{R$^2$ score}
                & \textbf{\BestAirborneSourceBelowDataVariableDepthScore}
                & \textbf{\BestAirborneBlockMedianSourcesVariableDepthScore}
                & \\
    \end{tabular}
\end{table*}

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c c l c c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values}
            & \textbf{Best}
            & \textbf{R$^2$ score} \\
        \toprule

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c c l c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values} \\
        \toprule

        \multirow{8}{*}{Source Below Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \AirborneSourceBelowDataConstantDepthDepth
                  \AirborneSourceBelowDataConstantDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBelowDataConstantDepthDamping
                  \AirborneSourceBelowDataConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \AirborneSourceBelowDataRelativeDepthDepth
                  \AirborneSourceBelowDataRelativeDepthDepthIncrement \\
            &
                & Damping
                & \AirborneSourceBelowDataRelativeDepthDamping
                  \AirborneSourceBelowDataRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \AirborneSourceBelowDataVariableDepthDepth
                  \AirborneSourceBelowDataVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneSourceBelowDataVariableDepthDepthFactor
                  \AirborneSourceBelowDataVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneSourceBelowDataVariableDepthKNearest
                  \AirborneSourceBelowDataVariableDepthKNearestIncrement \\
            &
                & Damping
                & \AirborneSourceBelowDataVariableDepthDamping
                  \AirborneSourceBelowDataVariableDepthDampingIncrement \\
        \midrule

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesConstantDepthDepth
                  \AirborneBlockMedianSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                  \AirborneBlockMedianSourcesConstantDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesConstantDepthDamping
                  \AirborneBlockMedianSourcesConstantDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesRelativeDepthDepth
                  \AirborneBlockMedianSourcesRelativeDepthDepthIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                  \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesRelativeDepthDamping
                  \AirborneBlockMedianSourcesRelativeDepthDampingIncrement \\
            \cmidrule{2-4}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesVariableDepthDepth
                  \AirborneBlockMedianSourcesVariableDepthDepthIncrement \\
            &
                & Depth factor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                  \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement \\
            &
                & K nearest
                & \AirborneBlockMedianSourcesVariableDepthKNearest
                  \AirborneBlockMedianSourcesVariableDepthKNearestIncrement \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                  \AirborneBlockMedianSourcesVariableDepthSpacingIncrement \\
            &
                & Damping
                & \AirborneBlockMedianSourcesVariableDepthDamping
                  \AirborneBlockMedianSourcesVariableDepthDampingIncrement \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                    & \AirborneGridSourcesConstantDepthDepth
                      \AirborneGridSourcesConstantDepthDepthIncrement \\
            &
                & Spacing (m)
                    & \AirborneGridSourcesConstantDepthSpacing
                      \AirborneGridSourcesConstantDepthSpacingIncrement \\
            &
                & Pad
                    & \AirborneGridSourcesConstantDepthPad
                      \AirborneGridSourcesConstantDepthPadIncrement \\
            &
                & Damping
                    & \AirborneGridSourcesConstantDepthDamping
                      \AirborneGridSourcesConstantDepthDampingIncrement \\
    \end{tabular}
\end{table*}

>>>>

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey. The table also contains the set of parameters
        that generates the best prediction for each source distribution and its
        corresponding R$^2$ score.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c c l c c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values}
            & \textbf{Best}
            & \textbf{R$^2$ score} \\
        \toprule

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey. The table also contains the set of
        parameters that generates the best prediction for each source
        distribution and its corresponding R$^2$ score.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c c l c c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values}
            & \textbf{Best}
            & \textbf{R$^2$ score} \\
        \toprule

        \multirow{8}{*}{Source Below Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \AirborneSourceBelowDataConstantDepthDepth
                  \AirborneSourceBelowDataConstantDepthDepthIncrement
                & \BestAirborneSourceBelowDataConstantDepthDepth
                & \multirow{2}{*}{
                    \BestAirborneSourceBelowDataConstantDepthScore
                  } \\
            &
                & Damping
                & \AirborneSourceBelowDataConstantDepthDamping
                  \AirborneSourceBelowDataConstantDepthDampingIncrement
                & \BestAirborneSourceBelowDataConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \AirborneSourceBelowDataRelativeDepthDepth
                  \AirborneSourceBelowDataRelativeDepthDepthIncrement
                & \BestAirborneSourceBelowDataRelativeDepthDepth
                & \multirow{2}{*}{
                    \BestAirborneSourceBelowDataRelativeDepthScore
                  } \\
            &
                & Damping
                & \AirborneSourceBelowDataRelativeDepthDamping
                  \AirborneSourceBelowDataRelativeDepthDampingIncrement
                & \BestAirborneSourceBelowDataRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \AirborneSourceBelowDataVariableDepthDepth
                  \AirborneSourceBelowDataVariableDepthDepthIncrement
                & \BestAirborneSourceBelowDataVariableDepthDepth
                & \multirow{4}{*}{
                    \BestAirborneSourceBelowDataVariableDepthScore
                  } \\
            &
                & Depth factor
                & \AirborneSourceBelowDataVariableDepthDepthFactor
                  \AirborneSourceBelowDataVariableDepthDepthFactorIncrement
                & \BestAirborneSourceBelowDataVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \AirborneSourceBelowDataVariableDepthKNearest
                  \AirborneSourceBelowDataVariableDepthKNearestIncrement
                & \BestAirborneSourceBelowDataVariableDepthKNearest
                & \\
            &
                & Damping
                & \AirborneSourceBelowDataVariableDepthDamping
                  \AirborneSourceBelowDataVariableDepthDampingIncrement
                & \BestAirborneSourceBelowDataVariableDepthDamping
                & \\
        \midrule

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesConstantDepthDepth
                  \AirborneBlockMedianSourcesConstantDepthDepthIncrement
                & \BestAirborneBlockMedianSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockMedianSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                  \AirborneBlockMedianSourcesConstantDepthSpacingIncrement
                & \BestAirborneBlockMedianSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockMedianSourcesConstantDepthDamping
                  \AirborneBlockMedianSourcesConstantDepthDampingIncrement
                & \BestAirborneBlockMedianSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesRelativeDepthDepth
                  \AirborneBlockMedianSourcesRelativeDepthDepthIncrement
                & \BestAirborneBlockMedianSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockMedianSourcesRelativeDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                  \AirborneBlockMedianSourcesRelativeDepthSpacingIncrement
                & \BestAirborneBlockMedianSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockMedianSourcesRelativeDepthDamping
                  \AirborneBlockMedianSourcesRelativeDepthDampingIncrement
                & \BestAirborneBlockMedianSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockMedianSourcesVariableDepthDepth
                  \AirborneBlockMedianSourcesVariableDepthDepthIncrement
                & \BestAirborneBlockMedianSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestAirborneBlockMedianSourcesVariableDepthScore
                  } \\
            &
                & Depth factor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                  \AirborneBlockMedianSourcesVariableDepthDepthFactorIncrement
                & \BestAirborneBlockMedianSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \AirborneBlockMedianSourcesVariableDepthKNearest
                  \AirborneBlockMedianSourcesVariableDepthKNearestIncrement
                & \BestAirborneBlockMedianSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                  \AirborneBlockMedianSourcesVariableDepthSpacingIncrement
                & \BestAirborneBlockMedianSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockMedianSourcesVariableDepthDamping
                  \AirborneBlockMedianSourcesVariableDepthDampingIncrement
                & \BestAirborneBlockMedianSourcesVariableDepthDamping
                & \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                & \AirborneGridSourcesConstantDepthDepth
                  \AirborneGridSourcesConstantDepthDepthIncrement
                & \BestAirborneGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestAirborneGridSourcesConstantDepthScore
                  } \\
            &
                & Spacing (m)
                & \AirborneGridSourcesConstantDepthSpacing
                  \AirborneGridSourcesConstantDepthSpacingIncrement
                & \BestAirborneGridSourcesConstantDepthSpacing
                & \\
            &
                & Pad
                & \AirborneGridSourcesConstantDepthPad
                  \AirborneGridSourcesConstantDepthPadIncrement
                & \BestAirborneGridSourcesConstantDepthPad
                & \\
            &
                & Damping
                & \AirborneGridSourcesConstantDepthDamping
                  \AirborneGridSourcesConstantDepthDampingIncrement
                & \BestAirborneGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}
